---
title: "Wendy's tweets analysis"
author: "Masha"
date: "6/4/2020"
output:  
   md_document:
    variant: markdown_github
---
libraries 
```{r}
library(rtweet)
library(twitteR)
library(stringr)
library(lubridate)
library(tm)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
TEXT AND SENTIMENTAL ANALYSIS FUNCTIONS
```{r}
load("C:/Users/fb8502oa/Desktop/Github stuff/Tweet-Analysis/TextFunctions.RData")
load("C:/Users/fb8502oa/Desktop/Github stuff/Tweet-Analysis/PosNeg.RData")
```

DATA
```{r}
load("C:/Users/fb8502oa/Desktop/Github stuff/Tweet-Analysis/Impeach.RData")
names(Impeach)
```

TWEET SUMMARY
```{r}
summary(Impeach$retweet_count)
summary(Impeach$favorite_count)
```
```{r}
#looking at the fav retweet
Impeach$text[Impeach$favorite_count==8991] # this is the most retweeted tweet
```

Summary: This is the most retweet and 'fav' tweet during the Trump's impeachment hearing.

"Vindman and Schiff are essentially acknowledging that Vindman was the whistleblower’s source. They’re also both saying that neither of them know who the whistleblower is. So they’re both lying.


TIME STAMP FOR THE TWEETS
```{r}
#time stamps for the tweets
Impeach$date = ymd_hms(Impeach$created_at)
Impeach$hour = hour(Impeach$date)+ minute(Impeach$date)/60
hist(Impeach$hour, main = "Time of The Day Impeach Tweets", xlab = "Hours of The Day,", col = "steelblue", breaks =24)
```

Summary:
Most of the tweets were created in the night time. From the 14th hour. of the day to the 18th hour.

DAYS OF THE WEEK.
```{r}
Impeach$day = weekdays(as.Date(Impeach$date))
Impeach$day = factor(Impeach$day, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
barplot(table(Impeach$day), col = "Steelblue", main = "Days: Impeachment Tweets")
```
Summary: 
People mostly tweeted on Tuesdays.
Trump's hearing started at 1pm on Tuesday.


TWEET CLEANING
```{r}
Impeach.clean1 = textScrubber(Impeach)
Impeach.clean1$text[1:20]
```

```{r}
Impeach.tweets = clean.text(Impeach.clean1$text)
Impeach.tweets[20:40]
```
Summary:
These tweets look clean enough.


Corpus cleaning 
```{r}
#loading the data as corpus
Impeach.tweets = Corpus(VectorSource(Impeach))

#Convert all text to lower case
Impeach.tweets = tm_map(Impeach.tweets, content_transformer(tolower))

# Remove punctuations
Impeach.tweets <- tm_map(Impeach.tweets, removePunctuation)

# Remove numbers
Impeach.tweets <- tm_map(Impeach.tweets, removeNumbers)

# Remove english common stopwords
Impeach.tweets <- tm_map(Impeach.tweets, removeWords, stopwords("english"))


# Text stemming
Impeach.tweets <- tm_map(Impeach.tweets, stemDocument)

```


Replacing some
```{r}
Space <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))

Impeach.tweets <- tm_map(Impeach.tweets, Space, "/")
Impeach.tweets <- tm_map(Impeach.tweets, Space, "@")
Impeach.tweets <- tm_map(Impeach.tweets, Space, "\\|")
Impeach.tweets <- tm_map(Impeach.tweets, stripWhitespace)

```

TMD
```{r}
Impeach.TDM = TermDocumentMatrix(Impeach.tweets)
Impeach.mat = as.matrix(Impeach.TDM)
Impeach.mat[1:10, 1:20]
```

Frequently used words
```{r}
word.freq = sort(rowSums(Impeach.mat), decreasing = T)
barplot(word.freq[15:25], xlab = "Frequently Used Words", ylab = "Word Frequency", col = "Steelblue")
```


```{r}
word.freq[1: 50]
```

```{r}
# Remove english common stopwords
Impeach.tweets <- tm_map(Impeach.tweets, removeWords, c(stopwords("english"), "will", "use","today", "can", "come", "think", "watch", "day", "app"))
```

```{r}
word.freq[1:30]
```

Summary:
These were some of the most frequently used words in people's tweets regarding the impeachment hearing.


Looking for word associations
```{r}
findAssocs(Impeach.TDM, "vindman",.99)
```

Summary:
These are all the words that were highly associated with Vindman


LETS USE ASSOCIATION RULES TO FIND MORE ASSOCIATIONS.

```{r}
library(arules)
library(arulesViz)
```

Transposing the matrix
```{r}
temp = Impeach.mat
Impeach.trans = as(temp, "transactions")
```

```{r}
temp[temp>1] = 1
Impeach.trans = as(temp, "transactions")
Impeach.rules = apriori(Impeach.trans, parameter = list(supp = 0.020))
```

I can have interactions because it would let me knit the code.
```{r}
plot(Impeach.rules, method = "graph")
```



FREQUENTLY USED WORDS WORDCLOUD
```{r}
library(wordcloud)
wordcloud(words = names(word.freq), freq = word.freq, min.freq = 1000, col = rainbow(1000))
```
